Stability of virtual aggregations of prosumers through diversification

### 2015-07-29 Article.tex
update

Directly mapping cliques to coalitions by this de-correlation oriented approach is thus not sufficient. It is indeed possible that adding agents to these cliques has the combined effect of increasing the expected production while decreasing its stability. The question revolves around measuring the benefits of this production surplus compared to the disadvantage having higher instability. This can be quantified by the marginal benefit of equation \ref{eq:marginal_benefit}.

@@

Figure \ref{fig:search} displays the evolution of the global utility and the number of involved agents during the course of the greedy algorithm \ref{alg:algo1}. The transition from invalid to valid coalitions is clearly visible on the blue diamond curve and occurs between iteration 10 and 15. After this transition, coalition's utilities improve slowly up to a maximum point.

>>>>

Directly mapping cliques to coalitions by this de-correlation oriented approach is thus not sufficient. It is indeed possible that adding agents to these cliques has the combined effect of increasing the expected production while decreasing its stability. The question revolves around measuring the benefits of this production surplus compared to the disadvantage of having coalition with high volatility. This can be quantified by the marginal benefit of equation \ref{eq:marginal_benefit}.

@@

Figure \ref{fig:search} displays the evolution of the global utility and the number of involved agents during the course of the greedy algorithm \ref{alg:algo1}. The transition from an invalid to a valid coalitions is clearly visible on the blue diamond curve and occurs between iteration 10 and 15. After this transition, coalition's utilities improve slowly up to a maximum point.
